---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

This page will walk through major projects I did in ANAL 503.

# Geospatial Visualization Assignment

```{r}
img <- magick::image_read('~/desktop/wordcloud.png')
plot(img) # or print(img)
```


The goal of this assignment is to visualize historical US election data and unemployment rates across US counties using choropleths. You will create three 3x2 panels of choropleths, one each for Texas, California and Pennsylvania. The rows will correspond to the years 2008, 2012 and 2016, and the columns will correspond to the percent of the vote received either the Democratic or Republican candidate for president (your choice), and the unemployment rate in that year.



## California Voting Maps



### third level header

Here's an even lower level header

# My second post (note the order)

